Dependent Object Types

### 2012-09-05 doc/candidacy/slides.tex
tribe first pass

>>>>

\begin{frame}{Tribe: Discussion}
\begin{itemize}
\item no virtual classes in Scala; its virtual types can emulate some (but not all) of the benefits
\item because of {\tt out} field, Tribe has limited cross-family inheritance
\item soundness? substitution lemma seems wrong when {\tt null} is
  substituted for a variable in an expression whose type contains
  that variable
\item aims to have decidable type-checking, but still not proved so
\end{itemize}
\end{frame}
